---
title: "Proliferation quantification"
output: html_document
---



Library load
```{r}
library(tidyverse)
library(scales)
library(ggExtra)
library(ggpubr)
library(rstatix)
```




##Preprocessing
Load files and organizing data
```{r}
nuclei.pre.table <- read.csv("Nuclei.csv", header = TRUE)
metadata <- read.csv("metadata.2.csv", header = TRUE)
nuclei.table <- nuclei.pre.table %>% select(ImageNumber, ObjectNumber, AreaShape_Area, Intensity_IntegratedIntensity_DNA, Intensity_IntegratedIntensity_EdU,Intensity_IntegratedIntensity_Alpha_actinin,Intensity_IntegratedIntensity_pHH3, Intensity_StdIntensity_DNA, Intensity_StdIntensity_EdU,Intensity_StdIntensity_Alpha_actinin,Intensity_StdIntensity_pHH3, Children_EdU_Count)
head(nuclei.table)
nuclei.table <- left_join(nuclei.table, metadata, by = c("ImageNumber" = "ImageNumber"))
nuclei.table <- arrange(nuclei.table, OrderNumber.2)
head(nuclei.table)
```

Down sampling all samples to be counting the same number of cells
```{r}
set.seed(42)
nuclei.table.condition.1 <- nuclei.table %>% filter(Condition == "0uM.rep1")
nuclei.table.condition.2 <- nuclei.table %>% filter(Condition == "0uM.rep2")
nuclei.table.condition.3 <- nuclei.table %>% filter(Condition == "0uM.rep3")
nuclei.table.condition.4 <- nuclei.table %>% filter(Condition == "2uM.rep1")
nuclei.table.condition.5 <- nuclei.table %>% filter(Condition == "2uM.rep2")
nuclei.table.condition.6 <- nuclei.table %>% filter(Condition == "2uM.rep3")
nuclei.table.condition.7 <- nuclei.table %>% filter(Condition == "4uM.rep1")
nuclei.table.condition.8 <- nuclei.table %>% filter(Condition == "4uM.rep2")
nuclei.table.condition.9 <- nuclei.table %>% filter(Condition == "4uM.rep3")

nuclei.table.condition.1 <-nuclei.table.condition.1[sample(1:nrow(nuclei.table.condition.1), 2000), ]
nuclei.table.condition.2 <-nuclei.table.condition.2[sample(2:nrow(nuclei.table.condition.2), 2000), ]
nuclei.table.condition.3 <-nuclei.table.condition.3[sample(3:nrow(nuclei.table.condition.3), 2000), ]
nuclei.table.condition.4 <-nuclei.table.condition.4[sample(4:nrow(nuclei.table.condition.4), 2000), ]
nuclei.table.condition.5 <-nuclei.table.condition.5[sample(5:nrow(nuclei.table.condition.5), 2000), ]
nuclei.table.condition.6 <-nuclei.table.condition.6[sample(6:nrow(nuclei.table.condition.6), 2000), ]
nuclei.table.condition.7 <-nuclei.table.condition.7[sample(7:nrow(nuclei.table.condition.7), 2000), ]
nuclei.table.condition.8 <-nuclei.table.condition.8[sample(8:nrow(nuclei.table.condition.8), 2000), ]
nuclei.table.condition.9 <-nuclei.table.condition.9[sample(9:nrow(nuclei.table.condition.9), 2000), ]
nuclei.table <- rbind(nuclei.table.condition.1,nuclei.table.condition.2,nuclei.table.condition.3,nuclei.table.condition.4,nuclei.table.condition.5,nuclei.table.condition.6,nuclei.table.condition.7,nuclei.table.condition.8,nuclei.table.condition.9)
write.csv(nuclei.table,"nucleitable.organized.trimmed.csv", row.names = FALSE)
write.csv(nuclei.table.condition.1,"nucleitable.condition1.csv", row.names = FALSE)
write.csv(nuclei.table.condition.2,"nucleitable.condition2.csv", row.names = FALSE)
write.csv(nuclei.table.condition.3,"nucleitable.condition3.csv", row.names = FALSE)
write.csv(nuclei.table.condition.4,"nucleitable.condition4.csv", row.names = FALSE)
write.csv(nuclei.table.condition.5,"nucleitable.condition5.csv", row.names = FALSE)
write.csv(nuclei.table.condition.6,"nucleitable.condition6.csv", row.names = FALSE)
write.csv(nuclei.table.condition.7,"nucleitable.condition7.csv", row.names = FALSE)
write.csv(nuclei.table.condition.8,"nucleitable.condition8.csv", row.names = FALSE)
write.csv(nuclei.table.condition.9,"nucleitable.condition9.csv", row.names = FALSE)


```





Quantify Percent EdU positive per replicate
```{r}
object.numbers.table <- nuclei.table %>% group_by(Condition)
object.numbers.table<- summarize(object.numbers.table, Total.Nuclei=sum(Children_EdU_Count >= 0), Edu.Positvie=sum(Children_EdU_Count > 0), Percent.EdU = Edu.Positvie/Total.Nuclei*100)
object.numbers.table <- left_join(object.numbers.table, metadata, by = c("Condition" = "Condition"))
object.numbers.table <- as.data.frame(object.numbers.table)
nuclei.table[,'ImageNumber']<-factor(nuclei.table[,'ImageNumber'])
metadata[,'ImageNumber']<-factor(metadata[,'ImageNumber'])
object.numbers.table[,'ImageNumber']<-factor(object.numbers.table[,'ImageNumber'])
#edu.table <- edu.table[-which(edu.table$ImageNumber == "2"), ]
#nuclei.table <- nuclei.table[-which(nuclei.table$ImageNumber == "2"), ]
object.numbers.table <- object.numbers.table[-which(object.numbers.table$OrderNumber.1 == 100), ]
#metadata <- metadata[-which(metadata$ImageNumber == "2"), ]
#object.numbers.table
head(object.numbers.table)
mean.object.numbers.table <- object.numbers.table %>% group_by(OrderNumber.1)
mean.object.numbers.table<- summarize(mean.object.numbers.table, mean.Percent.EdU = mean(Percent.EdU), sd = sd(Percent.EdU), NAME = Name)
#mean.object.numbers.table <- left_join(mean.object.numbers.table, metadata, by = c("OrderNumber" = "OrderNumber"))
#mean.object.numbers.table <- mean.object.numbers.table[-which(mean.object.numbers.table$OrderNumber == 100), ]
mean.object.numbers.table[is.na(mean.object.numbers.table)] = 0
mean.object.numbers.table
write.csv(object.numbers.table,"replicatespercentedupositive.csv", row.names = FALSE)
```


#Need to change which rows you want to keep for the bar graphs
```{r}
mean.object.numbers.table <- mean.object.numbers.table[c(1,4,7),]
mean.object.numbers.table
```







































##Graph Section








Bar graph for %Edu positive with mean and error bars
```{r}
Conditions <- mean.object.numbers.table$NAME
graph1<-ggplot(data=mean.object.numbers.table, aes(x=reorder(NAME, OrderNumber.1), y=mean.Percent.EdU, fill = NAME)) +
  geom_col(stat="identity")+
  geom_errorbar(aes(ymin=mean.Percent.EdU-sd, ymax=mean.Percent.EdU+sd), width=.2,position=position_dodge(.9))+
  theme_bw() +
  scale_fill_brewer(palette="Set1",name="Condition")+
  theme(axis.text.x = element_text(face="bold", size = 17),
          axis.text.y = element_text(face="bold",size = 17))+ 
  ggtitle("Percent of nuclei that \nare EdU Positive",)+
xlab("Condition") + ylab("Percent (%)")+ 
  theme(axis.title.y = element_text(size=17, face="bold")) +
  theme(axis.title.x = element_text(size=17, face="bold")) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  theme(plot.title = element_text(face="bold"))+
theme(legend.title = element_text(face="bold",size = 17))+
theme(legend.text = element_text(size = 20))

#ggsave('Percent Edu Positive Graph.pdf', plot = graph1, device = "pdf",dpi = 700,width = 20, height = 20, units = "cm")
ggsave('Percent Edu Positive Graph.png', plot = graph1, device = "png",dpi = 700)
graph1
```
```{r}
# Open PDF device
pdf("Percent Edu Positive Graph.pdf")
ggplot(data=mean.object.numbers.table, aes(x=reorder(NAME, OrderNumber.1), y=mean.Percent.EdU, fill = NAME)) +
  geom_col(stat="identity")+
  geom_errorbar(aes(ymin=mean.Percent.EdU-sd, ymax=mean.Percent.EdU+sd), width=.2,position=position_dodge(.9))+
  theme_bw() +
  scale_fill_brewer(palette="Set1",name="Condition")+
  theme(axis.text.x = element_text(face="bold", size = 17),
          axis.text.y = element_text(face="bold",size = 17))+ 
  ggtitle("Percent of nuclei that are EdU Positive",)+
xlab("Condition") + ylab("Percent (%)")+ 
  theme(axis.title.y = element_text(size=17, face="bold")) +
  theme(axis.title.x = element_text(size=17, face="bold")) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  theme(plot.title = element_text(face="bold"))+
theme(legend.title = element_text(face="bold",size = 17))+
theme(legend.text = element_text(size = 20))
# Close the PDF device
dev.off()
```












Making a %pHH3 by cut off in pHH3 intensity
```{r}
trial <- nuclei.table %>% group_by(Condition)
summarize.trial <- trial %>% summarize(Total.Nuclei=sum(Children_EdU_Count >= 0), pHH3.Positive=sum(Intensity_IntegratedIntensity_pHH3 >= 1000), Percent.pHH3 = pHH3.Positive/Total.Nuclei*100)
 summarize.trial <- left_join(summarize.trial, metadata, by = c("Condition" = "Condition"))
summarize.trial
summarize.trial <- as.data.frame(summarize.trial)
nuclei.table[,'ImageNumber']<-factor(nuclei.table[,'ImageNumber'])
metadata[,'ImageNumber']<-factor(metadata[,'ImageNumber'])
summarize.trial[,'ImageNumber']<-factor(summarize.trial[,'ImageNumber'])
summarize.trial <- summarize.trial[-which(summarize.trial$OrderNumber.1 == 100), ]
write.csv(summarize.trial,"replicatespercentpHH3positive.csv", row.names = FALSE)
mean.summarize.trial <- summarize.trial %>% group_by(OrderNumber.1)
mean.summarize.trial<- summarize(mean.summarize.trial, mean.Percent.pHH3 = mean(Percent.pHH3), sd = sd(Percent.pHH3), NAME = Name)
#mean.summarize.trial <- left_join(mean.summarize.trial, metadata, by = c("OrderNumber" = "OrderNumber"))
#mean.summarize.trial <- mean.summarize.trial[-which(mean.summarize.trial$OrderNumber == 100), ]
mean.summarize.trial[is.na(mean.summarize.trial)] = 0
#mean.summarize.trial <- mean.summarize.trial[!duplicated(mean.summarize.trial$mean.Percent.pHH3)]
mean.summarize.trial <- mean.summarize.trial[c(1,4,7),]
mean.summarize.trial
```

```{r}
mean.summarize.trial <- summarize.trial %>% group_by(OrderNumber.1)
mean.summarize.trial<- summarize(mean.summarize.trial, mean.Percent.pHH3 = mean(Percent.pHH3), sd = sd(Percent.pHH3), NAME = Name)
#mean.summarize.trial <- left_join(mean.summarize.trial, metadata, by = c("OrderNumber" = "OrderNumber"))
#mean.summarize.trial <- mean.summarize.trial[-which(mean.summarize.trial$OrderNumber == 100), ]
mean.summarize.trial[is.na(mean.summarize.trial)] = 0
#mean.summarize.trial <- mean.summarize.trial[!duplicated(mean.summarize.trial$mean.Percent.pHH3)]
mean.summarize.trial <- mean.summarize.trial[c(1,4,7),]
mean.summarize.trial
```


```{r}
graphphh3pos.bargraph<-ggplot(data=mean.summarize.trial, aes(x=reorder(NAME, OrderNumber.1), y=mean.Percent.pHH3, fill = NAME)) +
  geom_col(stat="identity")+
  geom_errorbar(aes(ymin=mean.Percent.pHH3-sd, ymax=mean.Percent.pHH3+sd), width=.2,position=position_dodge(.9))+
  theme_bw() +
  scale_fill_brewer(palette="Set1",name="Condition")+
  theme(axis.text.x = element_text(face="bold", size = 17),
          axis.text.y = element_text(face="bold",size = 17))+ 
  ggtitle("Percent of nuclei that \nare pHH3 Positive",)+
xlab("Condition") + ylab("Percent (%)")+ 
  theme(axis.title.y = element_text(size=17, face="bold")) +
  theme(axis.title.x = element_text(size=17, face="bold")) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  theme(plot.title = element_text(face="bold"))+
theme(legend.title = element_text(face="bold",size = 17))+
theme(legend.text = element_text(size = 20))

#ggsave('Percent Edu Positive Graph.pdf', plot = graph1, device = "pdf",dpi = 700,width = 20, height = 20, units = "cm")
ggsave('Percent pHH3 Positive Graph.png', plot = graphphh3pos.bargraph, device = "png",dpi = 700)
graphphh3pos.bargraph
```

```{r}
# Open PDF device
pdf("Percent pHH3 Positive Graph.pdf")
ggplot(data=mean.summarize.trial, aes(x=reorder(NAME, OrderNumber.1), y=mean.Percent.pHH3, fill = NAME)) +
  geom_col(stat="identity")+
  geom_errorbar(aes(ymin=mean.Percent.pHH3-sd, ymax=mean.Percent.pHH3+sd), width=.2,position=position_dodge(.9))+
  theme_bw() +
  scale_fill_brewer(palette="Set1",name="Condition")+
  theme(axis.text.x = element_text(face="bold", size = 17),
          axis.text.y = element_text(face="bold",size = 17))+ 
  ggtitle("Percent of nuclei that \nare pHH3 Positive",)+
xlab("Condition") + ylab("Percent (%)")+ 
  theme(axis.title.y = element_text(size=17, face="bold")) +
  theme(axis.title.x = element_text(size=17, face="bold")) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  theme(plot.title = element_text(face="bold"))+
theme(legend.title = element_text(face="bold",size = 17))+
theme(legend.text = element_text(size = 20))

# Close the PDF device
dev.off()
```



#need change
Y lim each time
Violin for Dapi Integrated intensity
```{r}

graph2 <- nuclei.table %>%  ggplot( aes(x=reorder(Name, OrderNumber.2), y=Intensity_IntegratedIntensity_DNA, fill = reorder(Name, OrderNumber.2))) + 
  geom_violin() +
  theme_bw()+
  scale_fill_brewer(palette="Set1", name="Condition")+
  theme(axis.text.x = element_text(face="bold", size = 14),
          axis.text.y = element_text(face="bold",size = 14))+ 
  ggtitle('Relative genomic content per nuclei')+
xlab("Condition") + ylab("Integrated Intensity")+
  theme(axis.title.y = element_text(size=14, face="bold")) +
  theme(axis.title.x = element_text(size=14, face="bold")) +
  theme(plot.title = element_text(face="bold"))+
  theme(plot.subtitle = element_text(size=14, face="bold"))+
  theme(legend.title = element_text(face="bold",size = 14))+
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  theme(legend.text = element_text(size = 14))+
  ylim(0,3000)

ggsave('Violin.Integrated.Intensity.dapi.png', plot = graph2, device = "png",dpi = 700)  
graph2   
  
```

```{r}
# Open PDF device
pdf("Violin.Integrated.Intensity.dapi.pdf")
nuclei.table %>%  ggplot( aes(x=reorder(Name, OrderNumber.2), y=Intensity_IntegratedIntensity_DNA, fill = reorder(Name, OrderNumber.2))) + 
  geom_violin() +
  theme_bw()+
  scale_fill_brewer(palette="Set1", name="Condition")+
  theme(axis.text.x = element_text(face="bold", size = 14),
          axis.text.y = element_text(face="bold",size = 14))+ 
  ggtitle('Relative genomic content per nuclei')+
xlab("Condition") + ylab("Integrated Intensity")+
  theme(axis.title.y = element_text(size=14, face="bold")) +
  theme(axis.title.x = element_text(size=14, face="bold")) +
  theme(plot.title = element_text(face="bold"))+
  theme(plot.subtitle = element_text(size=14, face="bold"))+
  theme(legend.title = element_text(face="bold",size = 14))+
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  theme(legend.text = element_text(size = 14))+
  ylim(0,3000)
# Close the PDF device
dev.off()
```


#need change
Y lim each time
Violin for Dapi Integrated intensity for EdU objects
```{r}
graph9 <-nuclei.table %>%  filter(Children_EdU_Count > 0) %>% ggplot( aes(x=reorder(Name, OrderNumber.2), y=Intensity_IntegratedIntensity_DNA, fill = reorder(Name, OrderNumber.2))) + 
  geom_violin() +
  theme_bw()+
  scale_fill_brewer(palette="Set1", name="Condition")+
  theme(axis.text.x = element_text(face="bold", size = 14),
          axis.text.y = element_text(face="bold",size = 14))+ 
  ggtitle('Dapi in EdU positive nuclei')+
xlab("Condition") + ylab("Integrated Intensity")+
  theme(axis.title.y = element_text(size=14, face="bold")) +
  theme(axis.title.x = element_text(size=14, face="bold")) +
  theme(plot.title = element_text(face="bold"))+
  theme(plot.subtitle = element_text(size=14, face="bold"))+
  theme(legend.title = element_text(face="bold",size = 14))+
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  theme(legend.text = element_text(size = 14))+
  ylim(0,3000)

ggsave('Violin.Integrated.Intensity.dapi.eduobjects.png', plot = graph9, device = "png",dpi = 700)  
graph9  
  
```

#need change
Violin for Dapi Integrated intensity for non EdU objects
```{r}
graph18 <-nuclei.table %>%  filter(Children_EdU_Count == 0) %>% ggplot( aes(x=reorder(Name, OrderNumber.2), y=Intensity_IntegratedIntensity_DNA, fill = reorder(Name, OrderNumber.2))) +
  geom_violin() +
  theme_bw()+
  scale_fill_brewer(palette="Set1",name = "Condition")+
  theme(axis.text.x = element_text(face="bold", size = 14),
          axis.text.y = element_text(face="bold",size = 14))+ 
  ggtitle('Dapi in EdU negative nuclei')+
xlab("Condition") + ylab("Integrated Intensity")+
  theme(axis.title.y = element_text(size=14, face="bold")) +
  theme(axis.title.x = element_text(size=14, face="bold")) +
  theme(plot.title = element_text(face="bold"))+
  theme(plot.subtitle = element_text(size=14, face="bold"))+
  theme(legend.title = element_text(face="bold",size=14))+
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  theme(legend.text = element_text(size = 14))+
  ylim(0,3000)

ggsave('Violin.Integrated.Intensity.dapi.noneduobjects.png', plot = graph18, device = "png",dpi = 700)  
graph18  
  
```


column for pairing violin plots 
#Need to change things based on the ordering file
```{r}
test.nuclei.table <- nuclei.table
test.nuclei.table$Children_EdU_Count <- as.integer(test.nuclei.table$Children_EdU_Count)
test.nuclei.table <- test.nuclei.table %>% filter(Children_EdU_Count<2)
test.nuclei.table$dapi.identifier <- paste(test.nuclei.table$Name,test.nuclei.table$Children_EdU_Count) 
ordering <- test.nuclei.table
ordering$dapi.identifier <- test.nuclei.table$dapi.identifier
ordering <- ordering[!duplicated(ordering$dapi.identifier), ]
ordering$OrderNumber.violinpaired <- c(1,2,3,4,6,5)
ordering <- ordering[,c(17,18)]
test.nuclei.table <- left_join(test.nuclei.table, ordering, by = c("dapi.identifier" = "dapi.identifier"))
head(test.nuclei.table)
```

testing putting violin plots next to eachother that are proliferative and nonproliferative
```{r}
graphparallel <-test.nuclei.table  %>% ggplot( aes(x=reorder(dapi.identifier, OrderNumber.violinpaired), y=Intensity_IntegratedIntensity_DNA, fill = reorder(Name, OrderNumber.2))) +
  geom_violin() +
  theme_bw()+
  scale_fill_brewer(palette="Set1",name = "Condition")+
  theme(axis.text.x = element_text(face="bold", size = 14),
          axis.text.y = element_text(face="bold",size = 14))+ 
  ggtitle('Relative genomic content per nuclei \nseperated by EdU incorperation')+
xlab("Condition") + ylab("Integrated Intensity")+
  theme(axis.title.y = element_text(size=14, face="bold")) +
  theme(axis.title.x = element_text(size=14, face="bold")) +
  theme(plot.title = element_text(face="bold"))+
  theme(plot.subtitle = element_text(size=14, face="bold"))+
  theme(legend.title = element_text(face="bold",size=14))+
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  theme(legend.text = element_text(size = 14))+
  ylim(0,3000)

ggsave('Violin.Integrated.Intensity.dapi.parallel.0equaleduneg.1equaledupos.png', plot = graphparallel, device = "png",dpi = 700)  
graphparallel
  
```
```{r}
# Open PDF device
pdf("Violin.Integrated.Intensity.dapi.parallel.0equaleduneg.1equaledupos.pdf")
test.nuclei.table  %>% ggplot( aes(x=reorder(dapi.identifier, OrderNumber.violinpaired), y=Intensity_IntegratedIntensity_DNA, fill = reorder(Name, OrderNumber.2))) +
  geom_violin() +
  theme_bw()+
  scale_fill_brewer(palette="Set1",name = "Condition")+
  theme(axis.text.x = element_text(face="bold", size = 14),
          axis.text.y = element_text(face="bold",size = 14))+ 
  ggtitle('Relative genomic content per nuclei \nseperated by EdU incorperation')+
xlab("Condition") + ylab("Integrated Intensity")+
  theme(axis.title.y = element_text(size=14, face="bold")) +
  theme(axis.title.x = element_text(size=14, face="bold")) +
  theme(plot.title = element_text(face="bold"))+
  theme(plot.subtitle = element_text(size=14, face="bold"))+
  theme(legend.title = element_text(face="bold",size=14))+
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  theme(legend.text = element_text(size = 14))+
  ylim(0,3000)# Close the PDF device
dev.off()
```



















Merging Violin Plots
```{r}
#ggarrange(graph1,graph2, graph9, graph18 + rremove("x.text"), 
 #         labels = c("A", "B", "C", "D"),
  #        ncol = 2, nrow = 2)





figure1 <- ggarrange(graph2+ rremove("x.text"), graphparallel+ rremove("x.text"), graph1+ rremove("x.text"), graphphh3pos.bargraph + rremove("x.text"),
          labels = c("A", "B", "C","D"),
          ncol = 2, nrow = 2,common.legend = TRUE, legend = "bottom")
figure1.merge <- annotate_figure(figure1,
                top = text_grob("Percent EdU and DNA content in CMs grown +/- CHIR", color = "black", face = "bold", size = 20),
                fig.lab = "Figure 1", fig.lab.face = "bold", fig.lab.size = 15)

ggsave('Figure1.dapi.and.percentedu.png', plot = figure1.merge, device = "png",dpi = 700,width = 30, height = 30, units = "cm")
figure1.merge


#ggarrange(bxp, dp, labels = c("A", "B"),
 #         common.legend = TRUE, legend = "bottom")

```
```{r}
# Open PDF device
pdf("Figure1.dapi.and.percentedu.pdf", width = 10, height = 8)
annotate_figure(figure1,
                top = text_grob("Percent EdU and DNA content in CMs grown +/- CHIR", color = "black", face = "bold", size = 20),
                fig.lab = "Figure 1", fig.lab.face = "bold", fig.lab.size = 15)
dev.off()
```


Merging Violin Plots Example
```{r}
#ggarrange(graph1,graph2, graph9, graph18 + rremove("x.text"), 
 #         labels = c("A", "B", "C", "D"),
  #        ncol = 2, nrow = 2)





#figure1 <- ggarrange(graph1,graph2, graph9, graph18 + rremove("x.text"), 
 #         labels = c("A", "B", "C", "D"),
  #        ncol = 2, nrow = 2,common.legend = TRUE, legend = "bottom")
#annotate_figure(figure1,
 #               top = text_grob("Visualizing mpg", color = "black", face = "bold", size = 24),
  #              bottom = text_grob("Data source: \n mtcars data set", color = "blue",
   #                                hjust = 1, x = 1, face = "italic", size = 10),
    #            left = text_grob("Figure arranged using ggpubr", color = "green", rot = 90),
     #           right = "I'm done, thanks :-)!",
      #          fig.lab = "Figure 1", fig.lab.face = "bold")






#ggarrange(bxp, dp, labels = c("A", "B"),
 #         common.legend = TRUE, legend = "bottom")

```













