---
title: "21.11.09 Cardiac.factors.PCM1.edu"
output: html_document
---

#Sections

##Preprocessing
##Graph Section

#This is a good example of how to make figures in R for publications
http://www.sthda.com/english/articles/24-ggpubr-publication-ready-plots/81-ggplot2-easy-way-to-mix-multiple-graphs-on-the-same-page/

#Statistics tests
https://www.r-bloggers.com/2017/06/add-p-values-and-significance-levels-to-ggplots/



Library load
```{r}
library(tidyverse)
library(scales)
library(ggExtra)
#library(ggpubr)
library(rstatix)
```

Search for all <#Potential change> for places that may need to be changed if you deviate from the initial pipeline methods
Search for all <#need change> that are unique things to each experiment usually titles



##Preprocessing
Load files and organizing data
```{r}
nuclei.pre.table <- read.csv("Nuclei.csv", header = TRUE)
metadata <- read.csv("metadata.2.csv", header = TRUE)
nuclei.table <- nuclei.pre.table %>% select(ImageNumber, ObjectNumber, AreaShape_Area, Intensity_IntegratedIntensity_DNA, Intensity_IntegratedIntensity_EdU,Intensity_IntegratedIntensity_Alpha_actinin,Intensity_IntegratedIntensity_pHH3, Intensity_StdIntensity_DNA, Intensity_StdIntensity_EdU,Intensity_StdIntensity_Alpha_actinin,Intensity_StdIntensity_pHH3, Children_EdU_Count)
head(nuclei.table)
nuclei.table <- left_join(nuclei.table, metadata, by = c("ImageNumber" = "ImageNumber"))
nuclei.table <- arrange(nuclei.table, OrderNumber.2)
head(nuclei.table)
```
Down sampling all samples to be counting the same number of cells


```{r}
set.seed(42)
nuclei.table.condition.1 <- nuclei.table %>% filter(Condition == "0uM.rep1")
nuclei.table.condition.2 <- nuclei.table %>% filter(Condition == "0uM.rep2")
nuclei.table.condition.3 <- nuclei.table %>% filter(Condition == "0uM.rep3")
nuclei.table.condition.4 <- nuclei.table %>% filter(Condition == "2uM.rep1")
nuclei.table.condition.5 <- nuclei.table %>% filter(Condition == "2uM.rep2")
nuclei.table.condition.6 <- nuclei.table %>% filter(Condition == "2uM.rep3")
nuclei.table.condition.7 <- nuclei.table %>% filter(Condition == "4uM.rep1")
nuclei.table.condition.8 <- nuclei.table %>% filter(Condition == "4uM.rep2")
nuclei.table.condition.9 <- nuclei.table %>% filter(Condition == "4uM.rep3")

nuclei.table.condition.1 <-nuclei.table.condition.1[sample(1:nrow(nuclei.table.condition.1), 2000), ]
nuclei.table.condition.2 <-nuclei.table.condition.2[sample(2:nrow(nuclei.table.condition.2), 2000), ]
nuclei.table.condition.3 <-nuclei.table.condition.3[sample(3:nrow(nuclei.table.condition.3), 2000), ]
nuclei.table.condition.4 <-nuclei.table.condition.4[sample(4:nrow(nuclei.table.condition.4), 2000), ]
nuclei.table.condition.5 <-nuclei.table.condition.5[sample(5:nrow(nuclei.table.condition.5), 2000), ]
nuclei.table.condition.6 <-nuclei.table.condition.6[sample(6:nrow(nuclei.table.condition.6), 2000), ]
nuclei.table.condition.7 <-nuclei.table.condition.7[sample(7:nrow(nuclei.table.condition.7), 2000), ]
nuclei.table.condition.8 <-nuclei.table.condition.8[sample(8:nrow(nuclei.table.condition.8), 2000), ]
nuclei.table.condition.9 <-nuclei.table.condition.9[sample(9:nrow(nuclei.table.condition.9), 2000), ]
nuclei.table <- rbind(nuclei.table.condition.1,nuclei.table.condition.2,nuclei.table.condition.3,nuclei.table.condition.4,nuclei.table.condition.5,nuclei.table.condition.6,nuclei.table.condition.7,nuclei.table.condition.8,nuclei.table.condition.9)
#write.csv(nuclei.table,"nucleitable.organized.trimmed.csv", row.names = FALSE)
#write.csv(nuclei.table.condition.1,"nucleitable.condition1.csv", row.names = FALSE)
#write.csv(nuclei.table.condition.2,"nucleitable.condition2.csv", row.names = FALSE)
#write.csv(nuclei.table.condition.3,"nucleitable.condition3.csv", row.names = FALSE)
#write.csv(nuclei.table.condition.4,"nucleitable.condition4.csv", row.names = FALSE)
#write.csv(nuclei.table.condition.5,"nucleitable.condition5.csv", row.names = FALSE)
#write.csv(nuclei.table.condition.6,"nucleitable.condition6.csv", row.names = FALSE)
#write.csv(nuclei.table.condition.7,"nucleitable.condition7.csv", row.names = FALSE)
#write.csv(nuclei.table.condition.8,"nucleitable.condition8.csv", row.names = FALSE)
#write.csv(nuclei.table.condition.9,"nucleitable.condition9.csv", row.names = FALSE)


```


```{r}
colnames(nuclei.table)
```
```{r}
# Define your phase categories based on Intensity_IntegratedIntensity_DNA
nuclei.table.phase <- nuclei.table %>%
  mutate(Phase = case_when(
    Intensity_IntegratedIntensity_DNA < 450 ~ "G1",
    Intensity_IntegratedIntensity_DNA >= 450 & Intensity_IntegratedIntensity_DNA < 550 ~ "S phase",
    Intensity_IntegratedIntensity_DNA >= 550 & Intensity_IntegratedIntensity_DNA < 900 ~ "G2/M",
    Intensity_IntegratedIntensity_DNA >= 900 ~ ">4n"
  ))
nuclei.table.phase <- nuclei.table.phase %>%
  mutate(EdU_Group = ifelse(Children_EdU_Count == 0, "Negative", "Positive"))

```


```{r}
# Summarize the counts for each Condition and Phase
summary_table <- nuclei.table.phase %>%
  group_by(Condition, EdU_Group) %>%
  mutate(
    Total_Count_Group = n()  # Calculate total count for each Condition and EdU_Group
  ) %>%
  group_by(Condition, EdU_Group, Phase) %>%
  summarise(
    Total_Count = n(),
    pHH3_Count = sum(Intensity_IntegratedIntensity_pHH3 > 1000),
    Phase_Percent = (Total_Count / first(Total_Count_Group)) * 100,  # Use total count for the group
    pHH3_Percent = pHH3_Count / Total_Count
  ) %>%
  ungroup()

# View the resulting dataframe
print(summary_table)
```


```{r}
# Write the summary_table to a .txt file
write.table(summary_table, file = "phase_summary_table.txt", sep = "\t", row.names = FALSE, quote = FALSE)

```

```{r}
write.table(nuclei.table.phase, file = "nuclei_table_phase_2000each.txt", sep = "\t", row.names = FALSE, quote = FALSE)
```

```{r}
# Loop over each unique Name
unique_names <- unique(nuclei.table.phase$Name)

for (name in unique_names) {
  # Filter for Children_EdU_Count = 0
  edu_neg <- nuclei.table.phase %>%
    filter(Name == name & Children_EdU_Count == 0)
  
  # Write to a .txt file if there are any rows
  if (nrow(edu_neg) > 0) {
    write.table(edu_neg, file = paste0(name, "_EdUneg_processed.txt"), sep = "\t", row.names = FALSE, quote = FALSE)
  }

  # Filter for Children_EdU_Count >= 1
  edu_pos <- nuclei.table.phase %>%
    filter(Name == name & Children_EdU_Count >= 1)
  
  # Write to a .txt file if there are any rows
  if (nrow(edu_pos) > 0) {
    write.table(edu_pos, file = paste0(name, "_EdUpos_processed.txt"), sep = "\t", row.names = FALSE, quote = FALSE)
  }
}

```

```{r}
# Loop over each unique Name
unique_names <- unique(nuclei.table.phase$Condition)

for (name in unique_names) {
  # Filter for Children_EdU_Count = 0
  edu_neg <- nuclei.table.phase %>%
    filter(Name == name & Children_EdU_Count == 0)
  
  # Write to a .txt file if there are any rows
  if (nrow(edu_neg) > 0) {
    write.table(edu_neg, file = paste0(name, "_EdUneg_processed.txt"), sep = "\t", row.names = FALSE, quote = FALSE)
  }

  # Filter for Children_EdU_Count >= 1
  edu_pos <- nuclei.table.phase %>%
    filter(Name == name & Children_EdU_Count >= 1)
  
  # Write to a .txt file if there are any rows
  if (nrow(edu_pos) > 0) {
    write.table(edu_pos, file = paste0(name, "_EdUpos_processed.txt"), sep = "\t", row.names = FALSE, quote = FALSE)
  }
}

```


```{r}
# Loop over each unique Condition
unique_conditions <- unique(nuclei.table.phase$Condition)

for (condition in unique_conditions) {
  # Filter for Children_EdU_Count = 0
  edu_neg <- nuclei.table.phase %>%
    filter(Condition == condition & Children_EdU_Count == 0)
  
  # Write to a .txt file if there are any rows
  if (nrow(edu_neg) > 0) {
    write.table(edu_neg, file = paste0(condition, "_EdUneg_processed.txt"), sep = "\t", row.names = FALSE, quote = FALSE)
  }

  # Filter for Children_EdU_Count >= 1
  edu_pos <- nuclei.table.phase %>%
    filter(Condition == condition & Children_EdU_Count >= 1)
  
  # Write to a .txt file if there are any rows
  if (nrow(edu_pos) > 0) {
    write.table(edu_pos, file = paste0(condition, "_EdUpos_processed.txt"), sep = "\t", row.names = FALSE, quote = FALSE)
  }
}

```


